\chapter{Results}\label{chap:results}

\section{TDM and MPC formats, CCSDS}\label{sec:tdm_ccsds}

	This section provides insight over standardised output data formats used in this work and encouraged by multinational agencies. 

\subsection{CCSDS}\label{subsec:ccsds}
	The Consultative Committee for Space Data Systems (CCSDS) is a multi-national forum formed by major space agencies to provide platform for discussion of common problems in the development, operation and maintenance of space data systems and is currently composed of 11 member agencies, 28 observer agencies and over 140 industrial associates \citep{ccsds}.

\subsection{TDM format}

	Tracking Data Message (TDM) is a standard message format for exchange of spacecraft tracking data between space agencies recommended by the CCSDS.
	
	TDM consists of lines with text on each line represented by ASCII characters. ASCII has been chosen because it is universally used and interpretable by all popular systems and human-readable without any necessary preprocessing, while only having a slight overhead when compared to binary in this context. TDM can be exchanged both in an XML format or a keyword-value notation (KVN) format.
	
	The structure of TDM KVN format has a header and a body and can be divided into three major parts:
	
	\begin{itemize}
		\item a header
		\item a metadata section (part of body)
		\item a data section (part of body).
	\end{itemize}
	
	Data section contains Tracking Data records which hold information about observations. Metadata section and data section added together are called a TDM segment. There is no explicit limit on the number of TDM segments in a body. See Table \ref{tab:TDMtable} for a detailed schematic.
	
\begin{table}[H]
\centering
\caption{TDM structure}
\label{tab:TDMtable}
\begin{tabular}{|c|c|c|c|}
\hline
Header                & \multicolumn{2}{c|}{}                   & mandatory                  \\ \hline
\multirow{8}{*}{Body} & \multirow{2}{*}{Segment 1} & Metadata 1 & \multirow{2}{*}{mandatory} \\ \cline{3-3}
                      &                            & Data 1     &                            \\ \cline{2-4} 
                      & \multirow{2}{*}{Segment 2} & Metadata 2 & \multirow{2}{*}{optional}  \\ \cline{3-3}
                      &                            & Data 2     &                            \\ \cline{2-4} 
                      & \multirow{2}{*}{...}       & ...        & \multirow{2}{*}{optional}  \\ \cline{3-3}
                      &                            & ...        &                            \\ \cline{2-4} 
                      & \multirow{2}{*}{Segment n} & Metadata n & \multirow{2}{*}{optional}  \\ \cline{3-3}
                      &                            & Data n     &                            \\ \hline
\end{tabular}
\end{table}
		
	\citep{TDMdefinition}
		
\subsection{MPC format}

	\citep{mpc}

\section{Visualization of results}\label{sec:visualization}

\section{Parameters}\label{sec:parameters}
